CS-B General Read Sequence Figure Generation

### 2022-06-15 R/CS-BGeneralReadSequenceFigureGeneration.rmd
Title text bugfix
Title was not pasted and was instead given as two arguments... Whoops!

```{r CPD_sequence_frequencies, fig.width = 11, fig.height = 10}
for (i in seq_along(CPDTGGSeqFreq)) {
  plotSequenceFrequencies(CPDTGGSeqFreq[[i]],
                          title = "CPD TGG Frequencies", repNames[i], expansionOffset = expansionOffset,
                          showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                          querySequences = c("TGG"))
}

for (i in seq_along(CPDCGASeqFreq)) {
  plotSequenceFrequencies(CPDCGASeqFreq[[i]],
                          title = "CPD CGA Frequencies", repNames[i], expansionOffset = expansionOffset,
                          showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                          querySequences = c("CGA"))
}
```

```{r 6-4_sequence_frequencies, fig.width = 11, fig.height = 10}
for (i in seq_along(sixFourTGGSeqFreq)) {
  plotSequenceFrequencies(sixFourTGGSeqFreq[[i]],
                          title = "6-4 TGG Frequencies", repNames[i], expansionOffset = expansionOffset,
                          showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                          querySequences = c("TGG"))
}

for (i in seq_along(sixFourCGASeqFreq)) {
  plotSequenceFrequencies(sixFourCGASeqFreq[[i]],
                          title = "6-4 CGA Frequencies", repNames[i], expansionOffset = expansionOffset,
                          showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                          querySequences = c("CGA"))
}
```

>>>>

```{r CPD_sequence_frequencies, fig.width = 11, fig.height = 10}
for (i in seq_along(CPDTGGSeqFreq)) {
  plotSequenceFrequencies(CPDTGGSeqFreq[[i]], title = paste("CPD TGG Frequencies", repNames[i]),
                          expansionOffset = expansionOffset, showThreePrimeCutSite = TRUE,
                          showFivePrimeCutSite = TRUE, querySequences = c("TGG"))
}

for (i in seq_along(CPDCGASeqFreq)) {
  plotSequenceFrequencies(CPDCGASeqFreq[[i]], title = paste("CPD CGA Frequencies", repNames[i]),
                          expansionOffset = expansionOffset, showThreePrimeCutSite = TRUE,
                          showFivePrimeCutSite = TRUE, querySequences = c("CGA"))
}
```

```{r 6-4_sequence_frequencies, fig.width = 11, fig.height = 10}
for (i in seq_along(sixFourTGGSeqFreq)) {
  plotSequenceFrequencies(sixFourTGGSeqFreq[[i]], title = paste("6-4 TGG Frequencies", repNames[i]),
                          expansionOffset = expansionOffset, showThreePrimeCutSite = TRUE,
                          showFivePrimeCutSite = TRUE, querySequences = c("TGG"))
}

for (i in seq_along(sixFourCGASeqFreq)) {
  plotSequenceFrequencies(sixFourCGASeqFreq[[i]], title = paste("6-4 CGA Frequencies", repNames[i]),
                          expansionOffset = expansionOffset, showThreePrimeCutSite = TRUE,
                          showFivePrimeCutSite = TRUE, querySequences = c("CGA"))
}
```
